---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# steamr

<!-- badges: start -->

[![R-CMD-check](https://github.com/maxikuehn/steamr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/maxikuehn/steamr/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of *steamr* is to visualize and process video game data from steam.

## Installation

You can install the development version of steamr from [GitHub](https://github.com/maxikuehn/steamr) with:

``` r
# install.packages("pak")
pak::pak("maxikuehn/steamr")
```

## Example

This is a basic example which shows you how you can access the games dataset:

```{r example games}
library(steamr)
head(games[, c("app_id", "name", "price", "metacritic")])
```

The exported function `avgpriceperyear` makes it easy to visualize the average price of game genres each year.

```{r games}
avgpriceperyear(games, selectedgenres = c("Action", "Indie", "Simulation"))
```

You can also create a S3 Object of a specific game:

```{r}
g <- get_game_details(72850)
print(g)
```
